Response to the defense feedback

### 2021-06-02 Chapter-6/Chapter-6.tex
Update Chapter-6.tex

Our tool can give a conservative estimation of the
side-channel leakage based on Channel Capacity. The channel capacity
measures the information flow between the source and the
destination. One useful characteristic of channel capacity is not
affected by the input, which is useful because we cannot
assume the input secrets of the software in practice. In the paper, we
use the sampling result to approximate the true value of the
channel capacity. We prove the sampling method presented in the paper can only give the conservative estimation of the amount of the true leakage.

>>>>

Our tool can give a conservative estimation of the
side-channel leakage based on Channel Capacity. The channel capacity
measures the information flow between the source and the
destination. One useful characteristic of channel capacity is not
affected by the input, which is useful because we cannot
assume the input secrets of the software in practice. In the chapter, we
use the sampling result to approximate the true value of the
channel capacity. We prove the sampling method presented in the chapter can only give the conservative estimation of the amount of the true leakage.
